The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-04 src/ms.tex
Word flow alterations

The \astropy code and ecosystem are more specialized than core scientific tools

@@

packages developed to enable specific research subdomains like

@@

  of the Project and overall coordination relies heavily on volunteer effort,
  but we therefore have significant amounts of critical infrastructure or core

@@

  Within the core package, a prime example is the \astropyfits subpackage, which

@@

  But also the specialized nature of the software requires being able to hire or

@@

  These challenges will require cultural and larger systemic changes to

@@

  Figure~\ref{fig:User-analytics-locations} shows the numnber of users per

@@

  countries and our maintainers and coordinators are fairly narrowly

@@

  We therefore need to develop more formal ways of engaging these communities in
  more democratic ways, such as through running and analyzing user surveys, or

>>>>

the \astropy code and ecosystem are more specialized than core scientific tools

@@

packages developed to enable research in specific subdomains such as

@@

  of the Project and overall coordination relies heavily on volunteer effort.
  We therefore have significant amounts of critical infrastructure or core

@@

  A prime example within the core package is the \astropyfits subpackage, which

@@

  Furthermore, the specialized nature of the software requires being able to hire or

@@

  These challenges will require both cultural and larger systemic changes to

@@

  Figure~\ref{fig:User-analytics-locations} shows the number of users per

@@

  countries, and our maintainers and coordinators are fairly narrowly

@@

  We therefore need to develop more formal and democratic ways of engaging these 
  communities, such as through running and analyzing user surveys, or
